---
title: "US_alcohol_consump_plotly"
author: "Tianjing Cai"
date: "12/15/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(data.table)
require(dplyr)
library(shiny)
require(tidyr)
require(data.table)
library(tidyverse)
library(DT)

library(ggplot2)
library(plotly)
library(igraph)
library(ggraph)
library(visNetwork)
library(networkD3)
```
```

```{r, echo = FALSE}
### plotly visualization on R
library(plotly)
alcohol_consump_person_us <- fread('../dataset/alcohol-consumption-per-person-us.csv')
title <- list(
  title = 'Alcohol consumption per person in U.S'
)
x <- list(
  title = 'Year'
)

y <- list(
  title = 'Alcohol consumption per person / litres'
)
p <- plot_ly(alcohol_consump_person_us, x = ~Year , mode = 'lines') %>% add_trace(y = ~alcohol_consump_person_us$`Beer (litres per person)`, type = 'scatter', name = 'Beer') %>% add_trace(y = ~alcohol_consump_person_us$`Wine (litres per person)`, type = 'scatter', name = 'Wine')  %>% add_trace(y = ~alcohol_consump_person_us$`Spirits (litres per person)`, type = 'scatter', name = 'Spirits') %>% layout(title = 'Alcohol consumption per person in U.S', xaxis = x, yaxis = y)

chart_link = api_create(p, filename="alcohol_consump_person_us")
chart_link
```